---
title: "Week 10 Report"
description: |
  Model for Charitable Donations as predicted by Age and Religious Group.
author:
  - name: Lia
date: 05-12-2021
output:
  distill::distill_article:
    self_contained: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      message = FALSE,
                      layout = "l-body-outset",
                      fig.width= 12,
                      fig.height= 10,
                      collapse =TRUE,
                       R.options = list(width = 60))
```

```{r 0.1, echo=FALSE}
### Libraries
library("tidyverse")
library("patchwork")
library("lubridate")
library("kableExtra")
library("gtsummary")
library("lubridate")
library("equatiomatic")
library("ggdag")
library("brms")
library("rstan")
library("rstanarm")
library("bayesplot")
library("easystats")
library("kableExtra")
library("broom")
library("tidybayes")
library("bmlm")
# if (!require(tidyLPA)) {
#   install.packages("tidyLPA")
# }
# rstan options
rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores ())
theme_set(theme_classic())
```

```{r 0.2, echo=FALSE}
nz_0 <- as.data.frame(readr::read_csv2(
  url(
    "https://raw.githubusercontent.com/go-bayes/psych-447/main/data/nzj.csv"
  )
))

# to relevel kessler 6 variables
f <-
  c(
    "None Of The Time",
    "A Little Of The Time",
    "Some Of The Time",
    "Most Of The Time",
    "All Of The Time"
  )



# get data into shape
df <- nz_0 %>%
  dplyr::mutate_if(is.character, factor) %>%
  select(
    -c(
      SWB.Kessler01,
      SWB.Kessler02,
      SWB.Kessler03,
      SWB.Kessler04,
      SWB.Kessler05,
      SWB.Kessler06
    )
  ) %>%
  dplyr::mutate(Wave = as.factor(Wave)) %>%
  dplyr::mutate(FeelHopeless = forcats::fct_relevel(FeelHopeless, f)) %>%
  dplyr::mutate(FeelDepressed = forcats::fct_relevel(FeelDepressed, f)) %>%
  dplyr::mutate(FeelRestless = forcats::fct_relevel(FeelRestless, f)) %>%
  dplyr::mutate(EverythingIsEffort = forcats::fct_relevel(EverythingIsEffort, f)) %>%
  dplyr::mutate(FeelWorthless = forcats::fct_relevel(FeelWorthless, f)) %>%
  dplyr::mutate(FeelNervous = forcats::fct_relevel(FeelNervous, f)) %>%
  dplyr::mutate(Wave = as.factor(Wave)) %>%
  dplyr::mutate(male_id = as.factor(Male)) %>%
  dplyr::mutate(date = make_date(year = 2009, month = 6, day = 30) + TSCORE) %>%
  dplyr::mutate(
    FeelWorthless_int = as.integer(FeelWorthless),
    FeelNervous_int =  as.integer(FeelNervous),
    FeelHopeless_int =  as.integer(FeelHopeless),
    EverythingIsEffort_int =  as.integer(EverythingIsEffort),
    FeelRestless_int =  as.integer(FeelRestless),
    FeelDepressed_int =  as.integer(FeelDepressed),
    HLTH.Fatigue_int = as.integer(HLTH.Fatigue + 1)
  ) %>%
  dplyr::mutate(yearS = TSCORE - min(TSCORE, na.rm = TRUE)) %>%
  dplyr::mutate(KESSLER6sum = as.integer(KESSLER6sum))
```

#  Write a varying intercept/varying slope model.

## Variables

CharityDonate

> How much money have you donated to charity in the last year?

### Predicted by 

Age

>  What is your age?

### Grouped by

BigDoms

> What religion or spiritual group? Christian, Buddhist, Muslim, Not Religious, Other

## Desrciptive Statistics

```{r 1.1, echo=FALSE}
# Create Model
df %>%
  dplyr::select(CharityDonate,
                Age,
                BigDoms) %>%
  gtsummary::tbl_summary(
    label = list(CharityDonate~"Annual Charitable Donations",
                  BigDoms~"Religious Group"),
    statistic = list(
      all_continuous() ~ "{mean} ({sd})"
    ),
    digits = all_continuous() ~ 2,
    missing_text = "(Missing)"
  ) %>%
   modify_header(label~"Variable")%>%
  modify_spanning_header(c("label","stat_0")~"Descriptive Statistics")%>%
  bold_labels()
```



```{r 1.2, echo=FALSE}
# Bar Graph
plot(df$BigDoms, main="Religious Groups")
```

```{r 1.3, echo=FALSE}
#Histogram
hist(df$Age, main="Age", xlab="Age")
```


## Results

The model used is multi level with group varying slopes

```{r 2.1, echo=FALSE}
# Create Model
m_vslopes  <-
  brm(
    CharityDonate ~ 1 + Age + (1 + Age | BigDoms),
    prior = c(
      prior(normal(5, 2), class = Intercept),
      prior(normal(-1, 10), class = b),
      prior(exponential(1), class = sd),
      prior(exponential(1), class = sigma),
      prior(lkj(2), class = cor)
    ),
    file = here::here("models", "multi-level-var-slopes"),
    data = df,
    family = gaussian)
summary(m_vslopes)
```

## Plots

```{r 2.2, echo=FALSE}
# Plot
p1 <- brms::mcmc_plot(m_vslopes)
p1
```

## Graph

```{r 2.3, echo=FALSE}
#Graphing Model
conditional_effects(m_vslopes)
```




We fitted a Bayesian linear mixed model (estimated using MCMC sampling with 4 chains of 2000 iterations and a warmup of 1000) to predict CharityDonate with Age (formula: CharityDonate ~ 1 + Age). The model included Age and BigDoms as random effects (formula: ~1 + Age | BigDoms). Priors over parameters were set as normal (mean = normal(-1, 10), SD = 10.00) distributions. The model's explanatory power is very weak (R2 = 8.92e-03, 89% CI [6.94e-03, 0.01], adj. R2 = 8.51e-03) and the part related to the fixed effects alone (marginal R2) is of 3.35e-04 (89% CI [2.44e-05, 6.95e-04]).  Within this model:

  - The effect of b_Intercept (Median = 394.20, 95% CI [141.02, 652.51]) has a 99.90% probability of being positive (> 0), 80.35% of being significant (> 281.90), and 0.00% of being large (> 1691.42). The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 4297)
  - The effect of b_Age (Median = -7.31, 95% CI [-12.20, -2.59]) has a 99.88% probability of being negative (< 0), 0.00% of being significant (< -281.90), and 0.00% of being large (< -1691.42). The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 4301)

Following the Sequential Effect eXistence and sIgnificance Testing (SEXIT) framework, we report the median of the posterior distribution and its 95% CI (Highest Density Interval), along the probability of direction (pd), the probability of significance and the probability of being large. The thresholds beyond which the effect is considered as significant (i.e., non-negligible) and large are |281.90| and |1691.42| (corresponding respectively to 0.05 and 0.30 of the outcome's SD). Convergence and stability of the Bayesian sampling has been assessed using R-hat, which should be below 1.01 (Vehtari et al., 2019), and Effective Sample Size (ESS), which should be greater than 1000 (Burkner, 2017).

## Conclusion

Age negatively predicted charitable donations. Individuals religious identities were correlated. 

\newpage

## Apendix

```{r Packages, ref.label='0.1', eval = FALSE}

```

```{r data, ref.label='0.2', eval = FALSE}

```

## Method

```{r desrciptive stats, ref.label='1.1', eval = FALSE}

```

```{r HistogramRel, ref.label='1.2', eval = FALSE}

```

```{r HistogramAge, ref.label='1.25', eval = FALSE}

```

## Results

```{r Model, ref.label='2.1', eval = FALSE}

```

```{r Plot, ref.label='2.2', eval = FALSE}

```


```{r graph, ref.label='2.3', eval = FALSE}

```



